1_bigsnpr_gwas_prep

### 2020-01-08 analysis/1_bigsnpr_gwas_prep.Rmd
Slide 18 edits for pairwise mash results

save_plot("Manhattan_FL50.png", plot = last_plot(), base_height = 4, base_asp = 2.5)

@@

library(ggcorrplot)
ggcorrplot(pairwise_plot$corr_matrix[c(4,6,8,7,2,5,3,1),c(4,6,8,7,2,5,3,1)])
save_plot("Pairwise_FL50_latitude.svg", plot = last_plot(), base_height = 2.5, base_asp = 1.618)

ggcorrplot(pairwise_plot2$corr_matrix[c(5,7,6,2,4,3,1),c(5,7,6,2,4,3,1)])
save_plot("Pairwise_T_GR_FL_latitude.svg", plot = last_plot(), base_height = 2.5, base_asp = 1.618)

ggcorrplot(pairwise_plot3$corr_matrix[c(5,8,10,7,9,2,6,3,4,1),c(5,8,10,7,9,2,6,3,4,1)])
save_plot("Pairwise_GR50_latitude.svg", plot = last_plot(), base_height = 2.5, base_asp = 1.618)

>>>>

save_plot("Manhattan_FL50.png", plot = last_plot(), base_height = 4, base_asp = 2.5)
```

# Pairwise plots GR FL
```{r}

@@

library(GGally)
pairplotFL <- mash_plot_pairwise_sharing(corrmatrix = pairwise_plot$corr_matrix[c(4,6,8,7,2,5,3,1),c(4,6,8,7,2,5,3,1)], reorder = FALSE)

corrplot1 <- ggcorr(data = NULL, cor_matrix = pairplotFL$corr_matrix, 
                       label = FALSE, label_alpha = TRUE,
                       label_size = 3, hjust = 0.95, vjust = 0.3,
                       layout.exp = 9, min_size = 0,
                       max_size = 3.5, limits = c(0,1), low = "#000077", mid = "#EEEEEE", high = "#FF5500")
save_plot("Pairwise_FL50_latitude_orange.svg", plot = corrplot1, base_height = 2.5, base_asp = 1.618)

ggcorr(data = NULL, cor_matrix = pairwise_plot2$corr_matrix[c(5,7,6,2,4,3,1),
                                                            c(5,7,6,2,4,3,1)], 
       label = FALSE, label_alpha = TRUE, label_size = 3, hjust = 0.95, 
       vjust = 0.3, layout.exp = 9, min_size = 0, max_size = 3.5, 
       limits = c(0,1), low = "#000077", mid = "#EEEEEE", high = "#FF5500")
save_plot("Pairwise_T_GR_FL_latitude_orange.svg", plot = last_plot(), base_height = 2.5, base_asp = 1.618)

ggcorr(data = NULL, cor_matrix = pairwise_plot3$corr_matrix[c(5,8,10,9,2,6,4,1),
                                                            c(5,8,10,9,2,6,4,1)], 
       label = FALSE, label_alpha = TRUE, label_size = 3, hjust = 0.95, 
       vjust = 0.3, layout.exp = 9, min_size = 0, max_size = 3.5, 
       limits = c(0,1), low = "#000077", mid = "#EEEEEE", high = "#FF5500")
save_plot("Pairwise_GR50_latitude_orange.svg", plot = last_plot(), base_height = 2.5, base_asp = 1.618)
